Brados: Declarative, Programmable Object Storage

### 2016-05-25 paper.tex
paper: minor edits
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In this paper, we propose a declarative approach to subservice composition
that allows programmers to focus on the high-level functional properties that
are required by applications.  Choosing an implementation that is consistent
with the declarative functional specification then can be posed as a search
problem over the space of parameters such as block sizes, storage interfaces
(e.g. key/value or block storage) and concurrency control mechanisms.  We
present experimental evaluation of our prototype, (etc etc)
\end{abstract}

@@

The top row of Figure~\ref{fig:jewel_v_firefly_v_es} shows the expected
performance of different sized log appends without metadata management overhead
using each of the five strategies defined in Table~\ref{tab:pd-map}.  Starting
with Jewel and 4KB entry sizes, we see that both one-to-one strategies have
relatively poor performance. Jewel with 1KB entry sizes sees a 2.5\(\times\)
performance increase for the \texttt{(N:1,KV)} mapping. The large period of reduced
throughput for corresponds to the OSD splitting file system directories in
order to maintain a maximum directory size, and will occur in \texttt{(1:1,KV)}
although the threshold number of objects is not reached in this example due to
the reduced overall throughput of the \texttt{(1:1,KV)} strategy.

@@

\textbf{Ceph Features}: to show the affect of cutting-edge Ceph features, we
now show results for BlueStore~\cite{weil:vault2016-bluestore}. BlueStore is a
replacement for the FileStore file system in the OSD (traditionally XFS).
FileStore has performance problems with transactions and enumerations; namely
the journal needed to assure atomicity incurs double writes and the file system
metadata model makes object listings slow, respectively. BlueStore stores data
directly on a block device and the metadata in RocksDB, which is provided by a
minimalistic, non-POSIX C++ filesystem. This model adheres to the overall
software defined storage strategy of Ceph because it gives the administrator
the flexibility to store the 3 components of BlueStore (e.g., data, RocksDB
database, and RocksDB write-ahead log) on any partition on any device in the
OSD.

>>>>

In this paper, we propose a declarative approach to subservice composition that
allows programmers to focus on the high-level functional properties that are
required by applications.  Choosing an implementation that is consistent with
the declarative functional specification then can be posed as a search problem
over the space of parameters such as block sizes, storage interfaces (e.g.
key/value or block storage) and concurrency control mechanisms. We base our
observations and conclusions on data mining the git repository of the Ceph
storage system and performance evaluating our own prototype implementations.
\end{abstract}

@@

The top row of Figure~\ref{fig:jewel_v_firefly_v_es} shows the expected
performance of different sized log appends without metadata management overhead
using each of the five strategies defined in Table~\ref{tab:pd-map}.  Starting
with Jewel and 4KB entry sizes, we see that both one-to-one strategies have
relatively poor performance. Jewel with 1KB entry sizes sees a 2.5\(\times\)
performance increase for the \texttt{(N:1,KV)} mapping. This particular graph
was extended to show an extra 30 minutes to demonstrate another disadvantage of
\texttt{(1:1,BS)} - the large period of reduced throughput corresponds to
the OSD splitting file system directories in order to maintain a maximum
directory size, and will occur in \texttt{(1:1,KV)} although the threshold
number of objects is not reached in this example due to the reduced overall
throughput of the \texttt{(1:1,KV)} strategy.

@@

\textbf{Ceph Features}: Ceph constantly adds new features and one particular
feature that has the potential to greatly improve the performance of log
appends is BlueStore~\cite{weil:vault2016-bluestore}. BlueStore is a
replacement for the FileStore file system in the OSD (traditionally XFS).
FileStore has performance problems with transactions and enumerations; namely
the journal needed to assure atomicity incurs double writes and the file system
metadata model makes object listings slow, respectively. BlueStore stores data
directly on a block device and the metadata in RocksDB, which is provided by a
minimalistic, non-POSIX C++ filesystem. This model adheres to the overall
software defined storage strategy of Ceph because it gives the administrator
the flexibility to store the 3 components of BlueStore (e.g., data, RocksDB
database, and RocksDB write-ahead log) on any partition on any device in the
OSD.

Unfortunately, due to space constraints, we do not show results for BlueStore.
Anecdotally, performance for reads was a couple thousand IOPs better while
writes are significantly worse. This is an example of a software feature that
has a good architecture for a CORFU application on Ceph but is not
production-ready yet.
